COVID19 - Forecast analysis

### 2020-03-12 draft_analysis_Italy.Rmd
Add home page, navigation and theme

The incubation period for the coronavirus is in mean 5.1 days with a range from 2-14 days.
Please se https://www.worldometers.info/coronavirus/coronavirus-incubation-period/.
In the calculation we considered an incubation period of 14 days for two reasons: 1) the majority are asymptomatic, contagiousness is greater than 5, maybe 14. A minority (who made the swab) will have a duration of about 5 days between the start of contagiousness and swab; 2) 14 days is the worst scenario to begin.
```{r r0 plot, echo=TRUE}
slope <-coef(summary(fit1))[2,1]; slope
slope.se <- coef(summary(fit1))[2,2]; slope.se
### R0 estimates and 95% IC 
R_0=slope*14+1;R_0
(slope+c(-1,1)*1.96*slope.se)*14+1
```
We want to make a short term forecast (14 days) with 3 scenario:  
-Scenario 1: 10 exposed people for each COVID-19 case and beta the same (no restrictions made or even no effects)
-Scenario 2: 10 exposed people for each COVID-19 case and beta reduced of 50% (-50% COVID19 contagious power)
-Scenario 3: 5 exposed people for each COVID-19 case and beta reduced of 50%  (-50% both exposed people and COVID19 contagious power)

>>>>

The incubation period for the coronavirus is in mean 5.1 days with a range from 2-14 days.
Please see https://www.worldometers.info/coronavirus/coronavirus-incubation-period/.
In the calculation we considered an incubation period of 14 days for two reasons: 1) the majority of cases is asymptomatic, contagiousness is greater than 5, maybe 14. A minority (who made the swab) will have a duration of about 5 days between the start of contagiousness and swab; 2) 14 days is the worst scenario to consider.
```{r r0 plot, echo=TRUE}
slope <-coef(summary(fit1))[2,1]; slope
slope.se <- coef(summary(fit1))[2,2]; slope.se
### R0 estimates and 95% IC 
R_0=slope*14+1;R_0
(slope+c(-1,1)*1.96*slope.se)*14+1
```
We want to make a short term forecast (14 days) with 3 scenario:  
-Scenario 1: 10 exposed people for each COVID-19 case and beta the same (no restrictions made or even no effects)
-Scenario 2: 10 exposed people for each COVID-19 case and beta reduced of 50% (-50% COVID19 contagious power)
-Scenario 3: 5 exposed people for each COVID-19 case and beta reduced of 50%  (-50% both exposed people and COVID19 contagious power)
